---
title: "Overview of the fars package"
author: "Shawn McKenzie"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"Overview of the fars package"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## INTRODUCTION

The fars package uses data from the US National Highway Traffic Safety Administration's
Fatality Analysis Reporting System, which is a nationwide census providing the American 
public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.
This package provides several functions to help you analyze and map this data. You can read 
more about the data by navigating to the following website:

https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars

## USAGE

The fars data has already been downloaded and included in this package.

The workflow you should follow is:

- Run the function `fars_summarize_years` to count the nunber of motor vehicle fatal injuries 
  for each month of each year
- Run the function `fars_map_state` to see a graphical map of the state that shows the location 
  of motor vehicle fatalities in the year

## OUTPUT OF `fars_summarize_years`

```{r summz}
head(fars::fars_summarize_years(2013:2015))
```

## OUTPUT OF `fars_map_state`

```{r show_map}
fars::fars_map_state(1,2015)
```

Please consult the package help pages for the usage, arguments, and details of each function.
