---
title: "Overview of the fars package"
author: "Shawn McKenzie"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


The functions provided for you in this assignment will be using data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. You can download the data for this assignment here:

fars_read
Read in a FARS file
This function reads in a file that has been downloaded from the US National Highway
Traffic Safety Administration's Fatality Analysis Reporting System (FARS).
https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars

make_filename
Make the FARS filename
This function constructs the FARS filename for the datafile of a selected year. The returned string
can be used as an input to fars_read.

fars_read_years
Aggregate FARS data across years
This function reads in one of more years of FARS data and aggregates the data into a list. Each
list element is a tibble for a specific year. Only the month and year columns are retained.

fars_summarize_years
Fatality counts
This function will count the nunber of motor vehicle fatal injuries for each month of each year

fars_map_state
Graphical map of state fatalities
This function produces a graphical map of the state and shows the location of motor vehicle
fatalities in the year. The map is then auto plotted to the plot window.


Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
